Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-08 paper/main.tex
Usage metrics: base

This section focuses on our corpus of \Corpus CRAN packages that use
\eval; these represent {\bf XX\%} of the entire repository. To provide
a picture of \eval usage, all runnable code in CRAN was executed. Runs
that did not exercise an \eval in the corpus were discarded. We
retained \Nbruns to generate the data presented here. In total,
\Allcalls invocations of \eval and its variants were recorded. Out of
the \Staticatleastonecallsite packages that use \eval, \Triggeredpkgs
packages were observed calling it in our runs --- the difference can
be chalked down to incomplete code coverage and occasional
infrastructure failures.

@@

\paragraph{Base}

>>>>

This section focuses on our corpus of \Corpus CRAN packages that use
\eval; these represent {\bf 28.9\%} of the entire repository. To provide % \Corpus / \CranAll 
a picture of \eval usage, all runnable code in CRAN was executed. Runs
that did not exercise an \eval in the corpus were discarded. We
retained \Nbruns to generate the data presented here. In total,
\Allcalls invocations of \eval and its variants were recorded. Out of
the \Staticatleastonecallsite packages that use \eval, \Triggeredpkgs
packages were observed calling it in our runs --- the difference can
be chalked down to incomplete code coverage and occasional
infrastructure failures.

@@

\paragraph{Base} The base dataset contains 13 packages. All of them trigger at least one \eval call. In total, \baseAllcalls \eval  were recorded. Most of them are calls to he normal \eval. There are a few calls to the other variants, less than 4\%. Contrary to the CRAN dataset, there are calls to \c{evalq} (\baseEvalqs). Out of \baseStaticeval static sites, \baseTriggeredeval are exercised, i.e. \baseTriggeredevalpct. Most of the arguments, \baseCodepercent,  are code objects. However, contrary to CRAN, few, only \baseSymbolpercent, are symbols, but rather language objects, \baseLanguagepercent. There are also few expression objects: \baseExpressionpercent.
The median argument size is \baseMedianszeval, which is more than for CRAN, which we dominated by symbol evaluation, whereas the maximum size is \baseMaxszeval. Small event evals (less than 50 events) amount for \baseSmalleventspct of the events in \eval calls.

% Figures for evalq are weird: more triggered than static call sites
